Interval Probability for Fuzzy Quantum Theories

### 2016-06-12 prob.tex
prob.tex \subsection{Measuring Quantum Probabilities} Starting...
prob.tex \subsection{Measuring Quantum Probabilities} Updates....

%%%%%
\subsection{Measuring Quantum Probabilities}
\amr{preparation fuzzy, device fuzzy, Meyer~\cite{PhysRevLett.83.3751}}

>>>>

%%%%%
\subsection{Measuring Quantum Probabilities}

If we adopt the frequency interpretation as in section~\ref{subsec:Measuring-Probabilities:-Buffon},
and measure the angular momentum for a spin-one particle in the Stern-Gerlach
experiment~\cite{FeynmanLeightonSands1965,Stern1988,peres1995quantum,544199}.
Ideally, if the local field strength directs to the $z$-axis, and
all particles have the same velocity, three spots will be produced
corresponding to $\ket{+Z}$, $\ket{0Z}$, and $\ket{-Z}$ predicted
by the semi-classical model assuming particles have definite trajectories.
In reality, all particles can from a hot oven cannot have the same
velocity, as the result, spots will be broader and more washed out
so that sometimes it may hard to decide a particle corresponding to
which state.

\amr{preparation fuzzy, device fuzzy, Meyer~\cite{PhysRevLett.83.3751}}
